---
title: "Visualization and EDA"
subtitle: Part 1
author: Yiyao LI
output: github_document
---

```{r setup}
library(tidyverse)
library(ggridges)
```

## load the weather data

```{r, warning=FALSE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


## Scatter plots

creat my first scatterplot ever.

```{r, warning=FALSE}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point()
```

New approach, same plot.

```{r, warning = FALSE}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()
```

Save and edit a plot project.

```{r, warning = FALSE}
weather_plot = 
  weather_df %>%
  ggplot(aes(x = tmin, y = tmax))

weather_plot + geom_point()
```

## Advanced scatter plot

Start with the same one and make it fancy

```{r, warning=FALSE}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point() + 
  geom_smooth(se = FALSE)
```

What about the 'aes' placement?

```{r, warning=FALSE}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = .2) + 
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)
```

combine some elements and form a new plot

```{r, warning=FALSE}
weather_df %>%
  ggplot(aes(x = date, y = tmax, color = name)) + 
  geom_point(aes(size = prcp), alpha = .5) + 
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)
```

How many geoms have to exist?

you can have whatever geoms you want

```{r, warning=FALSE}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_smooth(se = FALSE)
```

you can use a neat geom.

```{r, warning=FALSE}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_density2d() + 
  geom_point(alpha = .3)
```

## Univeriate plot

histogram is really great

```{r, warning=FALSE}
weather_df %>%
  ggplot(aes(x = tmin)) +
  geom_histogram()
```

add color

```{r, warning=FALSE}
weather_df %>%
  ggplot(aes(x = tmin, fill = name)) +
  geom_histogram() + 
  facet_grid(. ~ name)
```

try a new histogram

```{r, warning=FALSE}
weather_df %>%
  ggplot(aes(x = tmin, fill = name)) +
  geom_density(alpha = .3, adjust = .5)
```

box plots

```{r, warning=FALSE}
weather_df %>%
  ggplot(aes(x = name, y = tmin)) + 
  geom_boxplot()
```

Trend plot

```{r, warning=FALSE}
weather_df %>%
  ggplot(aes(x = name, y = tmin, fill = name)) + 
  geom_violin(alpha = .5) +
  stat_summary(fun = "median")
```

Ridge plot

```{r, warning = FALSE}
weather_df %>%
  ggplot(aes(x = tmin, y = name)) + 
  geom_density_ridges()
```

